Sushi monster

### 2025-02-13 inst/sushi.Rmd
better range for lambda

```{r tryH, cache=TRUE}
wanted <- sample(seq_len(nrow(a)), 10, replace=TRUE, prob=a[,1])
H1888 <- make_sushi_H(a[wanted,-1], strength=1.888)
H1000 <- make_sushi_H(a[wanted,-1], strength=1.000)
```

@@

```{r calclike, cache=TRUE}
f <- function(strength){
   H <- make_sushi_H(a[wanted,-1], strength=strength)
   maxp(H,give=1)$`Log-likelihood`
}
s <- seq(from=0.4,to=2,len=8)
L <- sapply(s,f)
```

>>>>

```{r tryH, cache=TRUE}
wanted <- sample(seq_len(nrow(a)), 500, replace=TRUE, prob=a[,1])
H1888 <- make_sushi_H(a[wanted,-1], strength=1.888)
H1000 <- make_sushi_H(a[wanted,-1], strength=1.000)
```

@@

```{r calclikesushi, cache=TRUE}
f <- function(strength){
   H <- make_sushi_H(a[wanted,-1], strength=strength)
   maxp(H,give=1)$`Log-likelihood`
}
s <- seq(from=1.4,to=7.5,len=5)
L <- sapply(s,f)
```
